Git Learning Notes

### 2015-03-29 ch-wox/ch-wox.tex
Final

In a typical non-seeded experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder was positioned in the upstream end of a quartz boat, and downstream about 2.5 inch the substrate was stationed. 
% cvd NW growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{CVD_and_temp.jpg}
\caption[\ce{WO3} NW CVD growth]{\ce{WO3} NW CVD growth and the temperature profile. The nominal NWs growth temperature were estimated according to the interpolation data. Zero inch location is defined at the upstream edge of furnace.}
\label{fig:wogrow}
\end{figure}
The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side. The substrate cleaning procedures have been elucidated on page~\pageref{ch2sub}. The boat was then loaded into the reaction chamber in a way that the powder source was placed in the center of the heating zone, and the substrate upstream end was aligned at 6.5 inch, as defined in Fig.~\ref{fig:wogrow}. After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr. The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool to room temperature.

@@

To study the growth mechanism, controlled experiments were performed on the oxidation of the tungsten seed particles dispersed on the substrate. In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone, and the sealed chamber was pumped down to an ultimate pressure of $\sim8$ mTorr. Then oxygen flow, varying between 1 sccm to 10 sccm, was admitted from the upstream inlet. With 10 sccm UHP Ar (99.999\%) as carrier gas, the overall pressure reached to about 100 mTorr. The heating temperature (500 to 750 \si{\degreeCelsius}) was ramped up in 30 min and lasted for 30 min; then, the heating power was turned off, and the chamber was allowed to naturally cool to room temperature.

@@

The growth dynamics of each source were investigated in the non-seeded growth. In each experiment, the temperature, flow rate, source, and substrate locations were controlled. Another parameter the author found important is the growth number\footnote{Defined as the order of growth performed in the same reaction chamber} in the same reaction chamber. Usually, one will conduct several runs in the same chamber, and different results may arise with respect to the growth number. With this degree of freedom included, the primary features of the deposition and the associated parameters were summarized in Table~\ref{tab:wot}.
%
\begin{table}[htb]
\centering
\caption{\ce{WO_x} ordinary transport results}\label{tab:wot}
\begin{tabular}{lp{2in}p{2in}r}
\toprule
\multicolumn{2}{c}{Growth Number} \\
\cmidrule(l){2-3}
 Source   & First & Second and more & Sodium(ppm)   \\
\midrule
3N      & Morphology from high to low temperature: islands, dense layer and a few NWs & Dense wires become more and more, sodium tungsten oxides phases dominate & 20  \\
3N5     & islands in high temperature end and layers in low temperature end & NA &      NA\\
4N5     & dense islands, some tiny wires in low temperature end & NA & 0.065 \\
5N      & similar to those of 4N5  & NA & 0.05\\
\bottomrule
\end{tabular}
\end{table}

The change of metallic W source after growth carries important information about the growth. So before examining the deposition on substrates, the SEM images of all powders before and after growth were presented in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
% powder before growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{pd_before.jpg}
\caption[SEM images of W powder before growth]{SEM images of W powder before growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N, respectively.}
\label{fig:pdbefore}
\end{figure}
Tungsten metal crystallizes in body center cubic (BCC) phase. Overall, the facets were still discernible. The 4N5 and 5N powders shared similar appearance and size distribution (Fig.~\ref{fig:pdbefore}c-d). In contrast, 3N powders were almost half the size of 3N5 ones and had more uniform size distribution as well. Absolute size and its distribution played a key role in its usage as seed, as discussed in Section~\ref{sec:sgfg}.
% powder after growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{pd_after.jpg}
\caption[SEM images of W powder after growth]{SEM images of W powder after growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
\label{fig:pdafter}
\end{figure}
After growth, 4N5 and 5N powder (Fig.~\ref{fig:pdafter}c-d) both developed the round edges, while 3N and 3N5 powders (Fig.~\ref{fig:pdafter}a-b) became bundled rods. This difference mainly arose from the average size, which dictated the degree of oxidation. Another possible reason was the presence of foreign elements in each W powders. As indicated by the certificate of analysis from corresponding vendors, carbon, nickel, iron, and sodium amounts up to tens of ppm in low purity W source.

The sodium contents in 3N powders fundamentally changed the deposition in ordinary transport growth. Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate were shown in Fig.~\ref{fig:nawoxsemedx}a. The nanostructures were \glspl{nw} with lengths up to several hundred microns and diameters about 40 to 500 nm. The deposition of nanowires was generally located on the substrates with the growth temperature ranging from 660 to 420 \si{\degreeCelsius}. Enlarged view at higher magnification revealed some nanowires were cylindrical and some were bundled belt. Rectangular microplate structures grew at lower temperature end of substrate, as displayed in Fig.~\ref{fig:nawoxsemedx}b and inset. The chemical compositions of the deposition were analyzed using \gls{edx}. A representative \gls{edx} spectrum in Fig.~\ref{fig:nawoxsemedx}c show the existence of W, Na, O, and Si signals in the specimen, where the Si signal was from the substrate. The crystal structures of the as-synthesized specimens were examined using XRD. The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide, as indicated on Fig.~\ref{fig:nawoxsemedx}d. The two sodium tungsten oxide phases were the triclinic \ce{Na5W_{14}O_{44}} phase (ICDD PDF 04-012-4449, \emph{a}=7.2740 \si{\angstrom}, \emph{b}=7.2911 \si{\angstrom}, \emph{c}=18.5510 \si{\angstrom}, $\alpha$=96.37$^\circ$, $\beta$=90.89$^\circ$, $\gamma$=119.65$^\circ$) and the triclinic \ce{Na2W4O_{13}} phase (ICDD PDF 04-012-7108, \emph{a}=11.1630 \si{\angstrom}, \emph{b}=3.8940 \si{\angstrom}, \emph{c}=8.2550 \si{\angstrom}, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$). The tungsten oxide was the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \si{\angstrom}, \emph{b}=7.53889 \si{\angstrom}, \emph{c}=7.6896 \si{\angstrom}, $\beta$=90.89$^\circ$).

@@

Micro-Raman spectroscopy was also carried out at room temperature in ambient atmosphere to confirm the phases of the microplates and ultra-long nanowires. Fig.~\ref{fig:nawoxram}a show the m-Raman spectrum of the microplates. The Raman lines at 949, 794-777, 366-263 \si{cm^{-1}} closely matched the reported \ce{Na2W4O_{13}} Raman shift.\cite{Fomichev1992} The Raman spectrum from the ultra-long nanowires was shown in Fig.~\ref{fig:nawoxram}b. The spectrum show major peaks in 100-150 \si{cm^{-1}}, 650-900 \si{cm^{-1}}, and 900-100 \si{cm^{-1}} regions. As compared to the reported peak positions (shown by reference lines in Fig.~\ref{fig:nawoxram}b), the nanowires consisted of only little amount of \ce{WO3} or \ce{Na2W4O_{13}} phase. Major peaks at 107, 695, 765, 913, 943, and 965 \si{cm^{-1}} cannot be assigned to reference in literatures. According to XRD and TEM analyses, the nanowires were mainly \ce{Na5W_{14}O_{44}}; therefore these peaks should belong to the \ce{Na5W_{14}O_{44}} phase. So far no Raman spectrum has been reported for this phase, hence this is probably the first observed Raman pattern for \ce{Na5W_{14}O_{44}}.
% nawox raman
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{nawox_raman_series}
\caption[Raman spectra on sodium tungsten oxides sample]{Raman spectra of (a) microplates matching the reported peak positions of the \ce{Na2W4O_{13}} phase, and (b) nanowires with comparisons to the reported major peak positions of \ce{WO3} (shown by black line) and \ce{Na2W4O_{13}} (shown by red line) phases.}
\label{fig:nawoxram}
\end{figure}

@@

% W-O bond length
\begin{table}[htb]
\centering
\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
\begin{tabular}{cccc}
\toprule
Fitted center (\si{cm^{-1}}) & length (\AA) & Fitted center (\si{cm^{-1}}) & length (\AA) \\
\midrule
694.6 & 1.900 &  808.6 &  1.821 \\
745.4 & 1.863 &  911.5 &  1.758 \\
764.4 & 1.850 &  933.0 &  1.745 \\
778.7 & 1.840 &   943.5 & 1.740 \\
788.4 & 1.834 &   965.4 & 1.728 \\
\bottomrule
\end{tabular}
\end{table}
For a comprehensive comparison purpose, the Raman fingerprints of various tungsten oxides and tungstate was shown in Table~\ref{tab:woram2}. 
\begin{table}[htb]
\centering
\caption{Raman fingerprints of tungsten oxides and sodium tungsten oxides}\label{tab:woram2}
\begin{tabular}{lp{3in}r}
\toprule
Phase & Raman Shift (\si{cm^{-1}}) &  Reference   \\
\midrule
\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
\ce{Na2W4O13} & 263(w), 272(w), 311(w), 366(w), 777(vs), 794(s), 949(m) &\cite{Fomichev1992}\\
\ce{Na5W14O44} & 107(s),695(m), 765(vs), 913(w), 943(m), 965(m)& this work\\
\bottomrule
\end{tabular}

@@

Heated at elevated temperatures, the W precursor, quartz tube, and quartz boat were three possible sources for Na. The sodium concentration in 3N source was about 20 ppm, as provided by vendor.\footnote{Owing to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the capacity limit of typical EDX.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm, respectively. To verify the major source of Na content coming from 3N powder, control experiments were employed by using W source with higher purities (4N5 or 5N). These ultra-high purity W sources produced pure tungsten oxide deposition, and no Na content was detected by EDX. These results verified the Na content was mainly from the 3N W powders. In the non-seeded growth experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2}, and then the oxidized source was evaporated producing \ce{WO3} and other sub-stoichiometric tungsten oxide vapors. The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by
\begin{enumerate*}[label=\itshape\alph*\upshape)]
\item only small amount of the tungsten source was consumed during the growth; and
\item only the top layer of the tungsten source was oxidized showing a dark blue color after growth.
\end{enumerate*} Due to its low concentration, the exact composition of the Na content in the tungsten source was difficult to probe. However, the evaporation rate of the Na content was expected to be high when heated at 1000 \si{\degreeCelsius}. This assumption wais supported by the observation that no Na was found in the deposition along the whole substrate in control experiments using the used 3N W source. Put it in another way, this observation indicated that the majority of Na content was already evaporated in previous experiment. Hence, despite of its low concentration in the source, the total amount of Na-based vapors produced during the growth could be significant, resulting in the dominance of sodium tungsten oxide phases in the nanowire growth region.

@@

Typical morphologies of non-seeded growth using other powders were shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively. The common feature of these samples was the dominance of islands growth in upstream end and layers growth in downstream end. The exact dimension still show some minor difference, particularly in the low temperature region. The deposition with 4N5 and 5N powders had much smaller grain size than that with 3N5 powders.
% 3N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox3n5.jpg}
\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation from (a) high temperature, (b) intermediate temperature, to (c) low temperature.}
\label{fig:wox3n5}
\end{figure}

% 4N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox4n5.jpg}
\caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation from (a) high temperature and (b) intermediate temperature, to (c) low temperature. Growth with 5N powders have almost the same morphology with that of 4N5, and is not shown hereby.}
\label{fig:wox4n5}
\end{figure}
It was worth pointing out that there were some NWs growth in low temperature end associated with 4N5 growth(Fig.~\ref{fig:wox4n5}c), although not in large scale.

@@

Commercial available tungsten powders with different size were usually associated with purity variation as well. Four kinds of tungsten powders were used as precursor to prepare \ce{WO3} NWs, as already summarized in Table~\ref{tab:powder}. The dimensions of tungsten powder were obtained by measuring the average size in SEM graphs. A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence, and influence of oxygen partial pressure.

@@

Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder. At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs begun to grow. When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface. Further increase of temperature led to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures. It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{JAP-2column_Fig3.jpg}
\caption[W powder oxidation: size effect]{W powder oxidation: size effect. SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow. a) 17 $\mu$m, b) 32 $\mu$m, c) 3.3 $\mu$m, d) 1.5 $\mu$m.}
\label{fig:pdsize}
\end{figure}

Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions. In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface was primarily covered with sub-micron particles as well as some short tiny NWs; whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature. This dramatic difference could be explained in terms of surface energy and oxygen diffusion. With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lowered the energy barrier of oxidation.\cite{tungsten1999} It was logical to deduce that higher temperature or increased oxygen level might favored the NWs formation on 3N5 powder. When it came to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition. Since the size distribution of 3N powder was more uniform than that of 3N5 powder, this study used the former as seeds.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{JAP-2column_Fig2.jpg}
\caption[W powder oxidation: oxygen pressure]{W powder oxidation: oxygen pressure. SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm. The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
\label{fig:pdoxy}
\end{figure}

>>>>

In a typical non-seeded experiment (Fig.~\ref{fig:wogrow}), about 2 g tungsten powder (3N) was positioned in the upstream end of a quartz boat, and downstream about 2.5 inch the substrate was stationed. 
% cvd NW growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.6\textwidth]{CVD_and_temp.jpg}
\caption[\ce{WO3} NW CVD growth]{\ce{WO3} NW CVD growth and the temperature profile. The nominal NWs growth temperature were estimated according to the interpolation data. Zero inch location is defined at the upstream edge of furnace.}
\label{fig:wogrow}
\end{figure}
The substrates were p-type, boron-doped and [100]-orientated silicon with about 1 $\mu$m thermally-grown silicon oxide layer on the polished side. The substrate cleaning procedures have been elucidated on page~\pageref{ch2sub}. The boat was then loaded into the reaction chamber in a way that the powder source was placed in the center of the heating zone, and the substrate upstream end was aligned at 6.5 inch, as defined in Fig.~\ref{fig:wogrow}. After pumping down, 1 \gls{sccm} \ce{O2} and 10 sccm Ar were admitted into the chamber, respectively, after which the overall pressure read approximately 110 mTorr. The temperature ramped up to 1000 \si{\degreeCelsius} in 30 min and lasted for 4 h, and subsequently the apparatus was allowed to naturally cool to room temperature.

@@

To study the growth mechanism, controlled experiments were performed on the oxidation of the tungsten seed particles dispersed on the substrate. In a typical oxidation experiment, tungsten powders were loaded into the uniform heating zone at the center of the chamber, and the sealed chamber was pumped down to an ultimate pressure of $\sim8$ mTorr. Then oxygen flow, varying between 1 sccm to 10 sccm, was admitted from the upstream inlet. With 10 sccm UHP Ar (99.999\%) as carrier gas, the overall pressure reached to about 100 mTorr. The heating temperature (500 to 750 \si{\degreeCelsius}) was ramped up in 30 min and lasted for 30 min; then, the heating power was turned off, and the chamber was allowed to naturally cool to room temperature.

@@

The growth dynamics of each source were investigated in the non-seeded growth. In each experiment, the temperature, flow rate, source, and substrate locations were controlled. Another parameter the author found important is the growth number\footnote{Defined as the order of growth performed in the same reaction chamber} in the same reaction chamber. Usually, one will conduct several runs in the same chamber, and different results may arise with respect to the growth number. With this degree of freedom included, the primary features of the deposition and the associated parameters were summarized in Table~\ref{tab:wot}.
\begin{table}[htb]
\centering
\caption{\ce{WO3} non-seeded growth summary}\label{tab:wot}
\begin{tabular}{lp{2in}p{2in}r}
\toprule
\multicolumn{2}{c}{Growth Number} \\
\cmidrule(l){2-3}
 Source   & First & Second and more & Sodium(ppm)   \\
\midrule
3N      & Morphology from high to low temperature: islands, dense layer and a few NWs & Dense wires become more and more, sodium tungsten oxides phases dominate & 20  \\
3N5     & islands in high temperature end and layers in low temperature end & NA &      NA\\
4N5     & dense islands, some tiny wires in low temperature end & NA & 0.065 \\
5N      & similar to those of 4N5  & NA & 0.05\\
\bottomrule
\end{tabular}
\end{table}
The change of metallic W source after growth carries important information about the growth. So before examining the deposition on substrates, the SEM images of all powders before and after growth were presented in Fig.~\ref{fig:pdbefore} and Fig.~\ref{fig:pdafter}, respectively.
% powder before growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{pd_before.jpg}
\caption[SEM images of W powder before growth]{SEM images of W powder before growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N, respectively.}
\label{fig:pdbefore}
\end{figure}
Tungsten metal crystallizes in body center cubic (BCC) phase. Overall, the facets were still discernible. The 4N5 and 5N powders shared similar appearance and size distribution (Fig.~\ref{fig:pdbefore}c-d). In contrast, 3N powders were almost half the size of 3N5 ones and had more uniform size distribution as well. Absolute size and its distribution played a key role in its usage as seed, as discussed in Section~\ref{sec:sgfg}.
% powder after growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{pd_after.jpg}
\caption[SEM images of W powder after growth]{SEM images of W powder after growth for (a) 3N, (b) 3N5, (c) 4N5 and (d) 5N. }
\label{fig:pdafter}
\end{figure}
After growth, 4N5 and 5N powder (Fig.~\ref{fig:pdafter}c-d) both developed the round edges, while 3N and 3N5 powders (Fig.~\ref{fig:pdafter}a-b) became bundled rods. This difference mainly arose from the average size, which dictated the degree of oxidation. Another possible reason was the presence of foreign elements in each W powders. As indicated by the certificate of analysis from corresponding vendors, carbon, nickel, iron, and sodium amounts up to tens of ppm in low purity W source.

The sodium contents in 3N powders fundamentally changed the deposition in the non-seeded growth. Typical morphologies of the as-synthesized nanostructures grown on a \ce{SiO2}-Si substrate were shown in Fig.~\ref{fig:nawoxsemedx}a. The nanostructures were \glspl{nw} with lengths up to several hundred microns and diameters about 40 to 500 nm. The deposition of nanowires was generally located on the substrates with the growth temperature ranging from 660 to 420 \si{\degreeCelsius}. Enlarged view at higher magnification revealed some nanowires were cylindrical and some were bundled belt. Rectangular microplate structures grew at lower temperature end of substrate, as displayed in Fig.~\ref{fig:nawoxsemedx}b and inset. The chemical compositions of the deposition were analyzed using \gls{edx}. A representative \gls{edx} spectrum in Fig.~\ref{fig:nawoxsemedx}c show the existence of W, Na, O, and Si signals in the specimen, where the Si signal was from the substrate. The crystal structures of the as-synthesized specimens were examined using XRD. The diffraction peaks were carefully indexed and the deposition was identified as two phases of sodium tungsten oxides and one phase of tungsten oxide, as indicated on Fig.~\ref{fig:nawoxsemedx}d. The two sodium tungsten oxide phases were the triclinic \ce{Na5W_{14}O_{44}} phase (ICDD PDF 04-012-4449, \emph{a}=7.2740 \si{\angstrom}, \emph{b}=7.2911 \si{\angstrom}, \emph{c}=18.5510 \si{\angstrom}, $\alpha$=96.37$^\circ$, $\beta$=90.89$^\circ$, $\gamma$=119.65$^\circ$) and the triclinic \ce{Na2W4O_{13}} phase (ICDD PDF 04-012-7108, \emph{a}=11.1630 \si{\angstrom}, \emph{b}=3.8940 \si{\angstrom}, \emph{c}=8.2550 \si{\angstrom}, $\alpha$=90.60$^\circ$, $\beta$=131.36$^\circ$, $\gamma$=79.70$^\circ$). The tungsten oxide was the monoclinic \ce{WO3} phase (ICDD PDF 01-083-0950, \emph{a}=7.30084 \si{\angstrom}, \emph{b}=7.53889 \si{\angstrom}, \emph{c}=7.6896 \si{\angstrom}, $\beta$=90.89$^\circ$).

@@

Micro-Raman spectroscopy was also carried out at room temperature in ambient atmosphere to confirm the phases of the microplates and ultra-long nanowires. Fig.~\ref{fig:nawoxram}a show the Raman spectrum of the microplates. The Raman lines at 949, 794-777, 366-263 \si{cm^{-1}} closely matched the reported \ce{Na2W4O_{13}} Raman shift.\cite{Fomichev1992} The Raman spectrum from the ultra-long nanowires was shown in Fig.~\ref{fig:nawoxram}b. The spectrum show major peaks in 100-150 \si{cm^{-1}}, 650-900 \si{cm^{-1}}, and 900-100 \si{cm^{-1}} regions. As compared to the reported peak positions (shown by reference lines in Fig.~\ref{fig:nawoxram}b), the nanowires consisted of only little amount of \ce{WO3} or \ce{Na2W4O_{13}} phase. Major peaks at 107, 695, 765, 913, 943, and 965 \si{cm^{-1}} cannot be assigned to reference in literatures. According to XRD and TEM analyses, the nanowires were mainly \ce{Na5W_{14}O_{44}}; therefore these peaks should belong to the \ce{Na5W_{14}O_{44}} phase. So far no Raman spectrum has been reported for this phase, hence this is probably the first observed Raman pattern for \ce{Na5W_{14}O_{44}}.
% nawox raman
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{nawox_raman_series}
\caption[Raman spectra on sodium tungsten oxides sample]{Raman spectra of (a) microplates matching the reported peak positions of the \ce{Na2W4O_{13}} phase, and (b) nanowires with comparisons to the reported major peak positions of \ce{WO3} (shown by black line) and \ce{Na2W4O_{13}} (shown by red line) phases.}
\label{fig:nawoxram}
\end{figure}

@@

% W-O bond length
\begin{table}[htb]
\centering
\caption{\ce{W-O} bond length predication}\label{tab:nawobond}
\begin{tabular}{cccc}
\toprule
Fitted center (\si{cm^{-1}}) & length (\AA) & Fitted center (\si{cm^{-1}}) & length (\AA) \\
\midrule
694.6 & 1.900 &  808.6 &  1.821 \\
745.4 & 1.863 &  911.5 &  1.758 \\
764.4 & 1.850 &  933.0 &  1.745 \\
778.7 & 1.840 &   943.5 & 1.740 \\
788.4 & 1.834 &   965.4 & 1.728 \\
\bottomrule
\end{tabular}
\end{table}
For a purpose of comprehensive comparison, the Raman fingerprints of various tungsten oxides and tungstate were listed in Table~\ref{tab:woram2}. 
\begin{table}[htb]
\centering
\caption{Raman fingerprints of tungsten oxides and sodium tungsten oxides}\label{tab:woram2}
\begin{tabular}{lp{3in}r}
\toprule
Phase & Raman Shift (\si{cm^{-1}}) &  Reference   \\
\midrule
\ce{WO2}  & 287(s), 334(w), 514(m), 600(w), 621(w), 785(vs) & \cite{Ma2005} \\
\ce{W18O49}  & broad bands from 750 to 780 & \cite{Guo2012} \\
             &  267(s), 778(s), 969(m) & \cite{Liu2013d} \\
m-\ce{WO3}  & 131(m), 265(m), 327(m), 715(s), 807(vs) &  \cite{Salje1975a,Daniel1987} \\
h-\ce{WO3}  & 162(m), 253(m), 320(m), 645, 690(s), 817(vs) &  \cite{Daniel1987}\\
\ce{WO3.H2O}  & 230(m), 377(w), 428(w), 650(s), 816(vs), 946(vs) &  \cite{Daniel1987} \\
\ce{WO3.2H2O}  & 235, 268(m), 380(w), 662(s), 685(vs), 960(vs) & \cite{Daniel1987} \\
\ce{Na2WO4}  & 94(w), 314(vw), 377(m), 813(m), 930(vs) &  \cite{Lima2011} \\
\ce{Na2W2O7}  & 381(w), 422(w), 763(w), 835(s), 886(m), 948(m), 957(vs) &  \cite{Knee1979} \\
\ce{Na2W4O13} & 263(w), 272(w), 311(w), 366(w), 777(vs), 794(s), 949(m) &\cite{Fomichev1992}\\
\ce{Na5W14O44} & 107(s),695(m), 765(vs), 913(w), 943(m), 965(m)& this work\\
\bottomrule
\end{tabular}

@@

Heated at elevated temperatures, the W precursor, quartz tube, and quartz boat were three possible sources for Na. The sodium concentration in 3N source was about 20 ppm, as provided by vendor.\footnote{Owing to the non-uniform distribution of foreign elements, detection of sodium by EDX is possible although the concentration is below the capacity limit of typical EDX.} The Na concentrations in quartz tube and quartz boat (GE 214 quartz, Wilmad Labglass) were 1 ppm and 0.7 ppm, respectively. To verify the major source of Na content, control experiments were employed by using W source with higher purities (4N5 or 5N). These ultra-high purity W sources produced pure tungsten oxide deposition, and no Na content was detected by EDX. These results verified the Na content was mainly from the 3N W powders. In the non-seeded growth experiments, the W source was first slowly oxidized at 1000 \si{\degreeCelsius} with 1 sccm \ce{O2}, and then the oxidized source was evaporated producing \ce{WO3} and other sub-stoichiometric tungsten oxide vapors. The tungsten oxide vapors produced this way were limited by the slow oxidation, as indicated by
\begin{enumerate*}[label=\itshape\alph*\upshape)]
\item only small amount of the tungsten source was consumed during the growth; and
\item only the top layer of the tungsten source was oxidized showing a dark blue color after growth.
\end{enumerate*} Owing to its low concentration, the exact composition of the Na content in the tungsten source was difficult to probe; however, the evaporation rate of the Na content was expected to be high when heated at 1000 \si{\degreeCelsius}. This assumption was supported by the observation that no Na was found in the deposition along the whole substrate in control experiments using the used 3N W source. Put it in another way, this observation indicated that the majority of Na content was already evaporated in previous experiment. Hence, despite of its low concentration in the source, the total amount of Na-based vapors produced during the growth could be significant, resulting in the dominance of sodium tungsten oxide phases in the nanowire growth region.

@@

Typical morphologies of non-seeded growth using other powders were shown in Fig.~\ref{fig:wox3n5} and Fig.~\ref{fig:wox4n5}, respectively. The common feature of these samples was the dominance of islands growth in upstream end and layers growth in downstream end. The exact dimension still show some minor difference, particularly in the low temperature region. The deposition with 4N5 and 5N powders had much smaller grain size than that with 3N5 powders.
% 3N5 powder growth 082712
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox3n5.jpg}
\caption[SEM images of \ce{WO3} growth using 3N5 powder]{SEM images of \ce{WO3} growth using 3N5 powder showing the morphology variation at (a) 736 \si{\degreeCelsius}, (b) 590 \si{\degreeCelsius}, and (c) 400 \si{\degreeCelsius}.}
\label{fig:wox3n5}
\end{figure}

% 4N5 powder growth
\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{wox4n5.jpg}
\caption[SEM images of \ce{WO3} growth using 4N5 powder]{SEM images of \ce{WO3} growth using 4N5 powder showing the morphology variation at (a) 870 \si{\degreeCelsius} and (b) 750 \si{\degreeCelsius}, and (c) 408 \si{\degreeCelsius}. Growth with 5N powders exhibited almost the same morphology as that of 4N5 and is not shown hereby.}
\label{fig:wox4n5}
\end{figure}
It was worth pointing out that there were some NWs growth in low temperature end associated with 4N5 growth(Fig.~\ref{fig:wox4n5}c), although not in large scale.

@@

Commercial available tungsten powders with different size were usually associated with purity variation as well. Four kinds of tungsten powders were used as precursor to prepare \ce{WO3} NWs, as already summarized in Table~\ref{tab:powder}. The dimensions of tungsten powder were obtained by measuring the average size in SEM micrographs. A systematic investigation was performed on the oxidation behavior of tungsten powder to evaluate the temperature effect, size-dependence, and influence of oxygen partial pressure.

@@

Fig.~\ref{fig:pdtemp} illustrated the effect of temperature on the morphological change and surface nanowires formation of 3N powder. At 500 \si{\degreeCelsius}, most tungsten powder retained its original shape and a layer of tiny dense NWs began to grow. When temperature was increased to 600 \si{\degreeCelsius}, 3N powder started to crack with longer NWs on the isolated surface. Further increase of temperature led to irregular shapes of tungsten power and aggregation of NWs, giving rise to the nanorods and bunched or bundled structures. It could be determined from the morphology variation that the optimal seeded growth temperature for 3N powder was in the range of 600 to 650 \si{\degreeCelsius}.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{JAP-2column_Fig3.jpg}
\caption[W powder oxidation: size effect]{W powder oxidation: size effect. SEM graphs illustrating the oxidization of four different size of tungsten powders at 600~\si{\degreeCelsius} and 1 sccm oxygen flow. a) 17 $\mu$m, b) 32 $\mu$m, c) 3.3 $\mu$m, d) 1.5 $\mu$m.}
\label{fig:pdsize}
\end{figure}

Fig.~\ref{fig:pdsize} depicted the oxidation of different sizes of tungsten powder under the same experimental conditions. In contrast to the morphology of 3N powder shown in Fig.~\ref{fig:pdtemp}, 3N5 powder surface was primarily covered with sub-micron particles as well as some short tiny NWs; whereas 4N5 and 5N powder were thoroughly oxidized, showing branched flowers feature. This dramatic difference could be explained in terms of surface energy and oxygen diffusion. With smaller dimension, the increased surface-to-volume ratio and short diffusion path both lowered the energy barrier of oxidation.\cite{tungsten1999} When it came to seeded growth, however, the powder size distribution was an important factor to give uniform NWs deposition. Since the size distribution of 3N powder was more uniform than that of 3N5 powder (Fig.~\ref{fig:pdbefore}), this study used the former as seeds.
% seed optimal
\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{JAP-2column_Fig2.jpg}
\caption[W powder oxidation: oxygen pressure]{W powder oxidation: oxygen pressure. SEM graphs of 3N tungsten powder oxidization at 600 \si{\degreeCelsius} under different rates of oxygen flow: a) 1 sccm, b) 2 sccm, c) 3 sccm, d) 10 sccm. The oxygen partial pressures were 13 mTorr, 23 mTorr, 32 mTorr, and 82 mTorr, respectively with background pressure subtracted.}
\label{fig:pdoxy}
\end{figure}

Fig.~\ref{fig:pdoxy} depicted the morphology change of 3N powder with respect to varied oxygen partial pressure. When the oxygen flow was lower than 3 sccm, 3N powder almost stayed as the same with cracks separating the dense layer of NWs. When oxygen flow was increased to 10 sccm, the 3N powder exemplified an enlarged version of that for 4N5 or 5N powder under 1 sccm oxygen flow. This observation again was supported by the surface energy explanation.
